---
title: "Week 02: COVID Visualization Activity"
date: "September, 11 2023"
author: "**`[[`**Xiaojing Yang**`]]`**"
---

Today, we'll be working with a data set related to COVID.
This data is based on data from the the [COVID Tracking Project](https://covidtracking.com/).
I cleaned up this data and also added total populations from the 2020 for each of the relevant categories.
Note, due to differences in the way race and ethnicity are encoded in the census as compared to the the COVID Tracking Project, the population counts for LatinX may be somewhat inaccurate.

```{r load_data}
library(tidyverse)
load("CRDT Data.RData")
ls()
```

I've include 4 different data sets.
They all have the same data but have it represented in different ways.
Try using the different data sets and see which ones are good for making which plots.


```{r first_plot}

ggplot(covid_data_count, aes(x = date, y = Cases)) + geom_point()
```



If you want to only look at a specific state, you can do it like this.
For now, see what you can do just using `ggplot`.

```{r}
covid_data_count |> 
  filter(state == "MA") |> 
  ggplot(aes(x = date, y = Cases, color = race)) + geom_line()
```

1. Write code for a plot and describe what you observe?
```{r}
covid_data_count |> 
  filter(race == "Asian") |> 
  ggplot(aes(x = date, y = Deaths, color = state)) + geom_line()
```
I observed that the overall death in each stated all increased during December and January. In specific, California, compared to all other states, increased dramatically in January. 

2. Are there any conclusions you can draw?

California has the highest death rate during January, and lack of medical resources may be one of the reason that leaded to it. 

3. What were you not able to do due to not having the R knowledge?

Without R knowledge, it's hard for me to draw different graphs to see the relations between different variables in a short amount of time. 

4. What other data would be useful to better understand this data?

The deaths numbers each states monthly before the pandanmic started. 
